### 2016-02-23 paper.tex
Add 'vertical-axis' to title and remove 'with tapered blades'
Refine objective in introduction

{\Large \textbf\newline{Experimental Study of a Reference Model Cross-Flow
        Turbine with Tapered Blades}} \newline % Insert author names,
% affiliations
% and corresponding author email (do not
% include
% titles, positions, or degrees).
\\ Peter Bachant\textsuperscript{1,*}, Martin Wosnik\textsuperscript{1,*}, Budi
Gunawan\textsuperscript{2}, Vincent S. Neary\textsuperscript{2} \\ \bigskip
\bf{1} Center for Ocean Renewable Energy, University of New Hampshire, Durham,
NH, 03857, USA \\ \bf{2} Water Power Technologies, Sandia National Laboratories,
P.O. Box 5800, Albuquerque, New Mexico 87185-MS1124, USA \\ \bigskip

@@

The present study was motivated by the need to acquire a new experimental
dataset for the lower solidity RM2 turbine at sufficient Reynolds numbers to be
relevant to full-scale modeling. It was hypothesized that the parasitic losses
from rotor blade support struts could play an important role in overall turbine
performance, especially for a lower solidity turbine that operates at higher tip
speed ratios. Thus, the parasitic torque from strut drag was measured without
blades, then deliberately and significantly increased in the physical model to
provide data to investigate its importance. The velocity field in the near-wake
of the turbine was then measured to compare with measurements from a higher
solidity rotor in the same experimental setup \cite{Bachant2015-JoT}, and
provide validation data for numerical models that predict wake flows, which
determine turbine--turbine interaction and optimal spacing for turbine arrays.
This dataset, along with the code for processing and visualization, is publicly
available (licensed via Creative Commons CC-BY for data and MIT license for
code) as a Git repository on GitHub
(\url{https://github.com/UNH-CORE/RM2-tow-tank}) and as a citable archive with a
digital object identifier (DOI) \cite{Bachant2015-RM2-data}.

>>>>

{\Large \textbf\newline{Experimental Study of a Reference Model Vertical-Axis
        Cross-Flow Turbine}} \newline % Insert author names,
% affiliations
% and corresponding author email (do not
% include
% titles, positions, or degrees).
\\ Peter Bachant\textsuperscript{1,*}, Martin Wosnik\textsuperscript{1,*}, Budi
Gunawan\textsuperscript{2}, Vincent S. Neary\textsuperscript{2} \\ \bigskip
\bf{1} Center for Ocean Renewable Energy, University of New Hampshire, Durham,
NH, 03857, USA \\ \bf{2} Water Power Technologies, Sandia National Laboratories,
P.O. Box 5800, Albuquerque, New Mexico 87185-MS1124, USA \\ \bigskip

@@

The main objective of the present study was to acquire a new experimental
dataset for the RM2 turbine at sufficient Reynolds numbers to be relevant to
full-scale physical and numerical modeling. It was hypothesized that the
parasitic losses from rotor blade support struts could play an important role in
overall turbine performance, especially for a lower solidity turbine that
operates at higher tip speed ratios. Thus, the parasitic torque from strut drag
was measured without blades, then deliberately and significantly increased in
the physical model to provide data to investigate its importance. The velocity
field in the near-wake of the turbine was then measured to compare with
measurements from a higher solidity rotor in the same experimental setup
\cite{Bachant2015-JoT}, and to provide validation data for numerical models that
predict wake flows, which determine turbine--turbine interaction and optimal
spacing for turbine arrays. This dataset, along with the code for processing and
visualization, has been made publicly available (licensed via Creative Commons
CC-BY for data and MIT license for code) as a Git repository on GitHub
(\url{https://github.com/UNH-CORE/RM2-tow-tank}) and as a citable archive with a
digital object identifier (DOI) \cite{Bachant2015-RM2-data}.
